Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-02-23 presentation-plan/presentation-plan.tex
Explain the basic algorithm a little

>>>>

The paper presents the Robust FF (\texttt{RFF}) planner, which should solve the
issues. \texttt{RFF} first generates an initial plan from the initial state to
some goal using \texttt{FF} on a determination of the MDP\@. Then for each
state in the plan, the successors of that state are added too. This is
expanding the execution structure. For the new state the probability to reach
this state should be higher than a certain threshold and if \texttt{FF} does
not return a failure for this state and a certain goal.
